{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/education.tex
やはり data race analysis
ensure parens on malloc()/free()

		which can arise when many data-race candidates cause Quicksand to spawn many Landslide jobs,

@@

		who had been using {\tt new\_pages} to allocate thread stacks ``very close'' to the {\tt malloc} heap.

>>>>

		which can arise when many data race candidates cause Quicksand to spawn many Landslide jobs,

@@

		who had been using {\tt new\_pages} to allocate thread stacks ``very close'' to the {\tt malloc()} heap.

### 2018-12-26 thesis/landslide.tex
ensure parens on malloc()/free()

\item {\bf Memory analysis options}
\begin{itemize}
	\item {\tt PURE\_HAPPENS\_BEFORE=1} - select Pure Happens-Before (1) or Limited Happens-Before (2) (\cref{sec:background-hb});
		corresponds to {\tt -V}/{\tt -H} in \cref{sec:landslide-quicksand-options}.
	\item {\tt FILTER\_DRS\_BY\_TID=1} - configures whether to use the {\tt TID} parameter of {\tt data\_\allowbreak{}race} described above.
	\item {\tt FILTER\_DRS\_BY\_LAST\_CALL=0} - configures whether to use the {\tt LAST\_CALL} parameter of {\tt data\_race} described above.
	\item {\tt ALLOW\_LOCK\_HANDOFF=0} - configures lockset tracking to permit or disallow a lock taken by one thread to be released by another thread.%
		\footnote{If enabled, accesses performed by the second thread before unlocking will not be considered protected by that lock,
			as Landslide cannot infer what prior event abstractly represented the lock's ownership changing,
			leading to spurious data race reports.
			This could be solved in future work with a new annotation.}
	\item {\tt ALLOW\_REENTRANT\_MALLOC\_FREE=0} - allow two threads to be in {\tt malloc}, {\tt free}, or so on simultaneously without declaring it a bug.%
		\footnote{Used in Pintos, where those functions lock/unlock the heap mutex themselves rather than relying on a wrapper function to do so before invoking them.}
	\item {\tt TESTING\_MUTEXES=0} - configure ``mutex testing'' mode (1),
		in which the data race analysis will not consider a mutex's implementation to be protected by the mutex itself.
		In other words, the mutex's internal memory accesses will be flagged as data races,
		thereby enabling Landslide to verify the mutual exclusion property.
		Normally (0), Landslide assumes mutual exclusion is provided in order to efficiently find data races in the rest of the code.
		Quicksand will automatically set this option for P2s when {\tt -t mutex\_test} is specified.
\end{itemize}

@@

{\tt mem\_update()} serves as the main entrypoint for tracking heap allocations.
It's called every instruction to check for the boundaries of the {\tt malloc} library,
and behaves in a similar way to the scheduler state machine described above.
Then, {\tt mem\_check\_shared\_access()} checks
(after some elaborate manoeuvres to figure out whether to use the kernel- or userspace heap)
whether, if in the heap region, the memory is contained in a currently-allocated heap block,
reporting a bug if not.

@@

\begin{itemize}
	\item {\tt arbiter\_interested()} ({\tt arbiter.c})
		will automatically insert preemption points on {\tt intr\_disable()} and {\tt intr\_enable()} calls
		(immediately before and after the interrupt state is changed, respectively)
		(as long as they aren't part of the mutex implementation, which has preemption points of its own).
	\item {\tt lockset\_remove()} ({\tt lockset.c})
		will warn instead of panic if a lock is unlocked twice,
		to allow for double {\tt sema\_up()} in cases where the lock is actually a multi-use semaphore rather than a mutex.
	\item {\tt build.sh} will edit the {\tt bootfd.img} binary to implant the name of the test case to be run in the kernel's boot command.
	\item {\tt sched\_check\_pintos\_init\_sequence()} ({\tt schedule.c})
		will force the kernel to skip the {\tt timer\_calibrate()} and {\tt timer\_msleep()} routines
		used in I/O initialization.
	\item {\tt keep\_schedule\_inflight()} ({\tt schedule.c})
		will detect when an attempted thread switch is impossible
		because the timer handler's try-lock will fail,
		and will abort the interleaving early as if it never existed (which it shouldn't).
	\item {\tt sched\_update\_kern\_state\_machine()} ({\tt schedule.c})
		will:
		\begin{itemize}
			\llitem track invocations of {\tt timer\_sleep()} and {\tt list\_insert\_ordered()}
				to infer when a thread is sleeping rather than blocked automatically,
				rather than relying on the {\tt tell\_landslide\_sleeping()} annotation.
			\llitem allow {\tt sema\_up()} to reenter itself,
				which may happen when an IDE interrupt is taken when interrupts are re-enabled at the end of said function.
			\llitem handle interrupt disabling/enabling as an abstract global lock for the purposes of happens-before analysis.
		\end{itemize}
	\item {\tt sched\_update()} ({\tt schedule.c})
		will handle ``lock handoff'' of the abstract disable-interrupts lock
		during a context switch for happens-before analysis.
	\item {\tt memory.c} (various functions)
		will handle page allocations from the {\tt palloc} family of functions in a separate memory heap,
		allowing the usual allocator {\tt malloc} to allocate and free from {\tt palloc}'ed memory,
		and checking both allocation heaps when checking for use-after-frees.
	\item {\tt kern\_address\_in\_heap()} ({\tt kernel\_specifics.c})
		will ignore DMA accesses to the VGA console,
		which appear to be in Pintos's heap region.
	\item {\tt test\_update\_state()} ({\tt test.c})
		will use the boundaries of {\tt run\_test()} to denote the test lifecycle.
\end{itemize}

@@

\begin{itemize}
	\item {\tt landslide} is the outermost script invoked by Quicksand (or by a \cref{sec:landslide-directly} aficionado).
		It exports several key environment variables used by the other scripts,
		ensures the instrumentation is up-to-date,
		and launches the simulator.
	\item {\tt getfunc.sh} defines several functions commonly used by {\tt build.sh} and {\tt definegen.sh} to extract function or global variable addresses from the program binary.
	\item {\tt symbols.sh} defines the names of kernel functions that can be instrumented automatically without a corresponding manual annotation (e.g., {\tt malloc} and friends, the names of the {\tt tell\_landslide} family, various library helpers such as {\tt panic}).
	\item {\tt build.sh} ensures the build of Landslide is up-to-date,
		and processes any dynamic configuration options which don't require updating the build (\cref{sec:landslide-dynamicconfig})
		It verifies all required {\tt tell\_landslide} annotations are present,
		verifies all required {\tt config.\allowbreak{}landslide} options,
		processes the dynamic config options,
		checks whether or not {\tt definegen.sh} needs to be run again (via hashes stored in {\tt student\_specifics.h} of the program binary and static config options),
		and does so if necessary.
	\item {\tt definegen.sh} produces the
		%automatically-generated
		content of {\tt student\_specifics.h}.
		It repeatedly invokes the helpers defined in {\tt getfunc.sh}
		to find the addresses of both functions specified in the config options
		and functions whose names are known in advance.%
		\footnote{You might think it should invoke objdump but once and keep the output in a shell variable,
		but I tried that and it was mysteriously slower, so I gave up without ever figuring out why.}
	\item {\tt p2-basecode/import-p2.sh} and {\tt pintos/import-pintos.sh}
		are invoked by their respective setup scripts
		to copy the student implementation into their respective directories.
		\cref{sec:education-pebbles-instrumentation} and \cref{sec:education-pintos-instrumentation}
		describe their office in more detail.
\end{itemize}

@@

		Rejects stack trace 1 (last matching directive is to exclude {\tt malloc}),
		accepts stack trace 2 (last matching directive is to include {\tt mutex\_lock})
	\item
		{\tt within\_user\_function thr\_join}

@@

		Accepts both (last matching directive is to accept {\tt mutex\_lock()},
		regardless of {\tt main()})
\end{itemize}

>>>>

\item {\bf Memory analysis options}
\begin{itemize}
	\item {\tt PURE\_HAPPENS\_BEFORE=1} - select Pure Happens-Before (1) or Limited Happens-Before (2) (\cref{sec:background-hb});
		corresponds to {\tt -V}/{\tt -H} in \cref{sec:landslide-quicksand-options}.
	\item {\tt FILTER\_DRS\_BY\_TID=1} - configures whether to use the {\tt TID} parameter of {\tt data\_\allowbreak{}race} described above.
	\item {\tt FILTER\_DRS\_BY\_LAST\_CALL=0} - configures whether to use the {\tt LAST\_CALL} parameter of {\tt data\_race} described above.
	\item {\tt ALLOW\_LOCK\_HANDOFF=0} - configures lockset tracking to permit or disallow a lock taken by one thread to be released by another thread.%
		\footnote{If enabled, accesses performed by the second thread before unlocking will not be considered protected by that lock,
			as Landslide cannot infer what prior event abstractly represented the lock's ownership changing,
			leading to spurious data race reports.
			This could be solved in future work with a new annotation.}
	\item {\tt ALLOW\_REENTRANT\_MALLOC\_FREE=0} - allow two threads to be in {\tt malloc()}, {\tt free()}, or so on simultaneously without declaring it a bug.%
		\footnote{Used in Pintos, where those functions lock/unlock the heap mutex themselves rather than relying on a wrapper function to do so before invoking them.}
	\item {\tt TESTING\_MUTEXES=0} - configure ``mutex testing'' mode (1),
		in which the data race analysis will not consider a mutex's implementation to be protected by the mutex itself.
		In other words, the mutex's internal memory accesses will be flagged as data races,
		thereby enabling Landslide to verify the mutual exclusion property.
		Normally (0), Landslide assumes mutual exclusion is provided in order to efficiently find data races in the rest of the code.
		Quicksand will automatically set this option for P2s when {\tt -t mutex\_test} is specified.
\end{itemize}

@@

{\tt mem\_update()} serves as the main entrypoint for tracking heap allocations.
It's called every instruction to check for the boundaries of the {\tt malloc()} library,
and behaves in a similar way to the scheduler state machine described above.
Then, {\tt mem\_check\_shared\_access()} checks
(after some elaborate manoeuvres to figure out whether to use the kernel- or userspace heap)
whether, if in the heap region, the memory is contained in a currently-allocated heap block,
reporting a bug if not.

@@

\begin{itemize}
	\item {\tt arbiter\_interested()} ({\tt arbiter.c})
		will automatically insert preemption points on {\tt intr\_disable()} and {\tt intr\_enable()} calls
		(immediately before and after the interrupt state is changed, respectively)
		(as long as they aren't part of the mutex implementation, which has preemption points of its own).
	\item {\tt lockset\_remove()} ({\tt lockset.c})
		will warn instead of panic if a lock is unlocked twice,
		to allow for double {\tt sema\_up()} in cases where the lock is actually a multi-use semaphore rather than a mutex.
	\item {\tt build.sh} will edit the {\tt bootfd.img} binary to implant the name of the test case to be run in the kernel's boot command.
	\item {\tt sched\_check\_pintos\_init\_sequence()} ({\tt schedule.c})
		will force the kernel to skip the {\tt timer\_calibrate()} and {\tt timer\_msleep()} routines
		used in I/O initialization.
	\item {\tt keep\_schedule\_inflight()} ({\tt schedule.c})
		will detect when an attempted thread switch is impossible
		because the timer handler's try-lock will fail,
		and will abort the interleaving early as if it never existed (which it shouldn't).
	\item {\tt sched\_update\_kern\_state\_machine()} ({\tt schedule.c})
		will:
		\begin{itemize}
			\llitem track invocations of {\tt timer\_sleep()} and {\tt list\_insert\_ordered()}
				to infer when a thread is sleeping rather than blocked automatically,
				rather than relying on the {\tt tell\_landslide\_sleeping()} annotation.
			\llitem allow {\tt sema\_up()} to reenter itself,
				which may happen when an IDE interrupt is taken when interrupts are re-enabled at the end of said function.
			\llitem handle interrupt disabling/enabling as an abstract global lock for the purposes of happens-before analysis.
		\end{itemize}
	\item {\tt sched\_update()} ({\tt schedule.c})
		will handle ``lock handoff'' of the abstract disable-interrupts lock
		during a context switch for happens-before analysis.
	\item {\tt memory.c} (various functions)
		will handle page allocations from the {\tt palloc()} family of functions in a separate memory heap,
		allowing the usual allocator {\tt malloc()} to allocate and free from {\tt palloc()}ed memory,
		and checking both allocation heaps when checking for use-after-frees.
	\item {\tt kern\_address\_in\_heap()} ({\tt kernel\_specifics.c})
		will ignore DMA accesses to the VGA console,
		which appear to be in Pintos's heap region.
	\item {\tt test\_update\_state()} ({\tt test.c})
		will use the boundaries of {\tt run\_test()} to denote the test lifecycle.
\end{itemize}

@@

\begin{itemize}
	\item {\tt landslide} is the outermost script invoked by Quicksand (or by a \cref{sec:landslide-directly} aficionado).
		It exports several key environment variables used by the other scripts,
		ensures the instrumentation is up-to-date,
		and launches the simulator.
	\item {\tt getfunc.sh} defines several functions commonly used by {\tt build.sh} and {\tt definegen.sh} to extract function or global variable addresses from the program binary.
	\item {\tt symbols.sh} defines the names of kernel functions that can be instrumented automatically without a corresponding manual annotation (e.g., {\tt malloc()} and friends, the names of the {\tt tell\_landslide} family, various library helpers such as {\tt panic()}).
	\item {\tt build.sh} ensures the build of Landslide is up-to-date,
		and processes any dynamic configuration options which don't require updating the build (\cref{sec:landslide-dynamicconfig})
		It verifies all required {\tt tell\_landslide} annotations are present,
		verifies all required {\tt config.\allowbreak{}landslide} options,
		processes the dynamic config options,
		checks whether or not {\tt definegen.sh} needs to be run again (via hashes stored in {\tt student\_specifics.h} of the program binary and static config options),
		and does so if necessary.
	\item {\tt definegen.sh} produces the
		%automatically-generated
		content of {\tt student\_specifics.h}.
		It repeatedly invokes the helpers defined in {\tt getfunc.sh}
		to find the addresses of both functions specified in the config options
		and functions whose names are known in advance.%
		\footnote{You might think it should invoke objdump but once and keep the output in a shell variable,
		but I tried that and it was mysteriously slower, so I gave up without ever figuring out why.}
	\item {\tt p2-basecode/import-p2.sh} and {\tt pintos/import-pintos.sh}
		are invoked by their respective setup scripts
		to copy the student implementation into their respective directories.
		\cref{sec:education-pebbles-instrumentation} and \cref{sec:education-pintos-instrumentation}
		describe their office in more detail.
\end{itemize}

@@

		Rejects stack trace 1 (last matching directive is to exclude {\tt malloc()}),
		accepts stack trace 2 (last matching directive is to include {\tt mutex\_lock()}).
	\item
		{\tt within\_user\_function thr\_join}

@@

		Accepts both (last matching directive is to accept {\tt mutex\_lock()},
		regardless of {\tt main()}).
\end{itemize}

### 2018-12-26 thesis/overview.tex
ensure parens on malloc()/free()

The Pintos kernel architecture \cite{pintos} is used at several universities, including the University of Chicago, Berkeley, and Stanford.
Its basecode implements a rudimentary kernel, consisting of a context switcher, round-robin scheduler, locking primitives, and program loader,
upon which students add more features in several projects.
Most relevant to this thesis, the basecode provides the following functions/libraries, among others:
\begin{itemize}
	\item Semaphores (the basic concurrency primitive, implemented using direct scheduler calls): {\tt sema\_up()}, {\tt sema\_down()}, {\tt sema\_try\_down()};
	\item Locks (which wrap a 1-initialized semaphore), {\tt lock\_acquire()}, {\tt lock\_\allowbreak{}release()}, {\tt lock\_try\_acquire()};
	\item Condition variables (also implemented using scheduler calls): {\tt cond\_wait()}, {\tt cond\_\allowbreak{}signal()}, {\tt cond\_broadcast()}, with the same semantics as Pebbles P2 condvars;
	\item Basic round-robin scheduling facilities: {\tt thread\_block()} (a kernel-level analogue to Pebbles's {\tt deschedule}), {\tt thread\_yield()}
	\item Kernel thread lifecycle management, {\tt thread\_create()} and {\tt thread\_exit()}, including stack space memory management;
	\item Interrupt and fault handlers;
	\item A page allocator, {\tt palloc\_get\_page()}, {\tt palloc\_get\_multiple()}, {\tt palloc\_free\_page()}, and {\tt palloc\_free\_multiple()}.
\end{itemize}
Both Pebbles and Pintos basecodes offer a standard C library including {\tt malloc}, string-formatting, printing, et cetera.

@@

Some schools further offer a virtual memory project, extending the provided VM with a frame table and supplemental page table and fault handler \cite{standford-cs140,uchicago-cs230}, or supplemental HTTP server and {\tt malloc} assignments \cite{berkeley-cs162}.
\revisionminor{This thesis is not concerned with these assignments.
as they are are largely architectural/algorithmic projects rather than concurrency-oriented ones.}
The main concurrency challenges in Pintos projects arise from the {\em threads} and {\em userprog} assignments:
implementing a correct {\tt alarm} routine,
ensuring the priority scheduler remains safe in the presence of concurrent threads of the same priority,
and designing correct interactions between the {\tt wait} and {\tt exit} system calls.

>>>>

The Pintos kernel architecture \cite{pintos} is used at several universities, including the University of Chicago, Berkeley, and Stanford.
Its basecode implements a rudimentary kernel, consisting of a context switcher, round-robin scheduler, locking primitives, and program loader,
upon which students add more features in several projects.
Most relevant to this thesis, the basecode provides the following functions/libraries, among others:
\begin{itemize}
	\item Semaphores (the basic concurrency primitive, implemented using direct scheduler calls): {\tt sema\_up()}, {\tt sema\_down()}, {\tt sema\_try\_down()};
	\item Locks (which wrap a 1-initialized semaphore), {\tt lock\_acquire()}, {\tt lock\_\allowbreak{}release()}, {\tt lock\_try\_acquire()};
	\item Condition variables (also implemented using scheduler calls): {\tt cond\_wait()}, {\tt cond\_\allowbreak{}signal()}, {\tt cond\_broadcast()}, with the same semantics as Pebbles P2 condvars;
	\item Basic round-robin scheduling facilities: {\tt thread\_block()} (a kernel-level analogue to Pebbles's {\tt deschedule}), {\tt thread\_yield()}
	\item Kernel thread lifecycle management, {\tt thread\_create()} and {\tt thread\_exit()}, including stack space memory management;
	\item Interrupt and fault handlers;
	\item A page allocator, {\tt palloc\_get\_page()}, {\tt palloc\_get\_multiple()}, {\tt palloc\_free\_page()}, and {\tt palloc\_free\_multiple()}.
\end{itemize}
Both Pebbles and Pintos basecodes offer a standard C library including {\tt malloc()}, string-formatting, printing, et cetera.

@@

Some schools further offer a virtual memory project, extending the provided VM with a frame table and supplemental page table and fault handler \cite{standford-cs140,uchicago-cs230}, or supplemental HTTP server and {\tt malloc()} assignments \cite{berkeley-cs162}.
\revisionminor{This thesis is not concerned with these assignments.
as they are are largely architectural/algorithmic projects rather than concurrency-oriented ones.}
The main concurrency challenges in Pintos projects arise from the {\em threads} and {\em userprog} assignments:
implementing a correct {\tt alarm} routine,
ensuring the priority scheduler remains safe in the presence of concurrent threads of the same priority,
and designing correct interactions between the {\tt wait} and {\tt exit} system calls.

### 2018-12-26 thesis/quicksand.tex
ensure parens on malloc()/free()

Finally, I identified a particular class of false positive data race candidates
under the Limited Happens-Before analysis (\cref{sec:background-datarace})
in which the associated memory was recycled by re-allocation between the two accesses,
and claim that it is safe to completely disregard them when considering where to add new preemption points.
\Cref{fig:recycle} shows a common code pattern and interleaving which can expose such behaviour.
If the {\tt malloc} on line~4 returns the same address passed to {\tt free} on line~2,
then lines~1 and 7 will be flagged as a potential data race.
I term this a {\em reallocation false-positive data race candidiate}.
To the human eye, this is obviously a false positive:
reordering lines~4-7 before lines~1-2 will cause {\tt malloc} to return a different region of allocated memory,
in turn causing {\tt x} and {\tt y} to no longer collide.
In studying a similar pattern, the Eraser tool from prior work \cite{eraser}
found that Thread 2's logic usually corresponds to an initialization pattern,
but for generality I have added an arbitrary {\tt publish} action to the example on line~6.

@@

The ability to disregard reallocation false positives is unique to Iterative Deepening.
When limited to a single test execution, suppressing any data race candidate matching this pattern is unsound.
Consider the more unusual program in \Cref{fig:recycle-bug},
in which the memory is recycled the same way, but the racing access's address is not tied to {\tt malloc}'s return value.
Here, reordering lines~6-7 before line~3 will allow {\tt x} and {\tt x2} to race.
Discarding the data race report as a false positive after checking just this one execution
would overlook such a bug,
but Iterative Deepening is guaranteed to explore the alternate interleaving,
in which the true data race will show up without {\tt free()} and {\tt malloc()} interposing,
so it is safe to suppress at first, as I will prove in \cref{sec:quicksand-realloc}.
Moreover,
in the context of Iterative Deepening, being able to discard certain data race candidates
allows Quicksand to skip exploring some entire state spaces,
and hence run fewer Landslides overall;
this is analogous to DPOR's ability to skip equivalent interleavings within a single Landslide instance.
Upcoming in the evaluation, \cref{sec:quicksand-eval-verif}'s \Cref{tab:drstatistix}
will show how many redundant state spaces Quicksand is able to prune with this technique.

@@

The interface with the model checker has two parts.
First, when starting each job, Quicksand creates a configuration file declaring which preemption points to use,
plus other test-case-specific options such as
which preemption points to suppress (\cref{sec:landslide-pps}),
especially those arising from the {\tt malloc} lock (\cref{sec:quicksand-realloc}),
which functions DPOR and data race analysis should treat as trusted code (\cref{sec:landslide-config-landslide}),
whether to enable mutex-testing mode (\cref{sec:landslide-dynamicconfig}),
transactional memory (\cref{sec:tm-implementation}),
and so on.
This is done by {\tt run\_job()} in {\tt job.c}.

>>>>

Finally, I identified a particular class of false positive data race candidates
under the Limited Happens-Before analysis (\cref{sec:background-datarace})
in which the associated memory was recycled by re-allocation between the two accesses,
and claim that it is safe to completely disregard them when considering where to add new preemption points.
\Cref{fig:recycle} shows a common code pattern and interleaving which can expose such behaviour.
If the {\tt malloc()} on line~4 returns the same address passed to {\tt free()} on line~2,
then lines~1 and 7 will be flagged as a potential data race.
I term this a {\em reallocation false-positive data race candidiate}.
To the human eye, this is obviously a false positive:
reordering lines~4-7 before lines~1-2 will cause {\tt malloc()} to return a different region of allocated memory,
in turn causing {\tt x} and {\tt y} to no longer collide.
In studying a similar pattern, the Eraser tool from prior work \cite{eraser}
found that Thread 2's logic usually corresponds to an initialization pattern,
but for generality I have added an arbitrary {\tt publish} action to the example on line~6.

@@

The ability to disregard reallocation false positives is unique to Iterative Deepening.
When limited to a single test execution, suppressing any data race candidate matching this pattern is unsound.
Consider the more unusual program in \Cref{fig:recycle-bug},
in which the memory is recycled the same way, but the racing access's address is not tied to {\tt malloc()}'s return value.
Here, reordering lines~6-7 before line~3 will allow {\tt x} and {\tt x2} to race.
Discarding the data race report as a false positive after checking just this one execution
would overlook such a bug,
but Iterative Deepening is guaranteed to explore the alternate interleaving,
in which the true data race will show up without {\tt free()} and {\tt malloc()} interposing,
so it is safe to suppress at first, as I will prove in \cref{sec:quicksand-realloc}.
Moreover,
in the context of Iterative Deepening, being able to discard certain data race candidates
allows Quicksand to skip exploring some entire state spaces,
and hence run fewer Landslides overall;
this is analogous to DPOR's ability to skip equivalent interleavings within a single Landslide instance.
Upcoming in the evaluation, \cref{sec:quicksand-eval-verif}'s \Cref{tab:drstatistix}
will show how many redundant state spaces Quicksand is able to prune with this technique.

@@

The interface with the model checker has two parts.
First, when starting each job, Quicksand creates a configuration file declaring which preemption points to use,
plus other test-case-specific options such as
which preemption points to suppress (\cref{sec:landslide-pps}),
especially those arising from the {\tt malloc()} lock (\cref{sec:quicksand-realloc}),
which functions DPOR and data race analysis should treat as trusted code (\cref{sec:landslide-config-landslide}),
whether to enable mutex-testing mode (\cref{sec:landslide-dynamicconfig}),
transactional memory (\cref{sec:tm-implementation}),
and so on.
This is done by {\tt run\_job()} in {\tt job.c}.
